---
title: "World Value Survey Analysis"
author: "Kathryn Haglich"
date: "10/17/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
#R Markdown set up 
knitr::opts_chunk$set(echo = TRUE)

#my favorite libraries - if you get an error because you need to install these, that's your fault 
library(tidyverse)
library(readxl)
library(janitor)
library(magrittr)
library(esquisse)
library(shiny)
library(shinydashboard)
library(ggmosaic)

#also does the notin command that I like 
`%notin%` <- Negate(`%in%`)
```

```{r reading data in and turning it into data frame, include=FALSE}
US <- read_excel("US2011.xlsx")
Russia <-read_excel("Russia2011.xlsx")
Japan <- read_excel("Japan2010.xlsx")

US <- as.data.frame(US)
Russia <- as.data.frame(Russia)
Japan <- as.data.frame(Japan)

```

```{r remove columns of each country all same general info, include=FALSE}
#gets rid of weird repeat columns 
US <- US[,-1*c(1:4, 334:338, 387, 389, 430 )]
Russia <- Russia[,-1*c(1:4,334:338, 387, 389, 430 )]
Japan <- Japan[,-1*c(1:4,334:338, 387, 389 )]

#View(Russia[,4])

#View(Russia[279,])
#View(Russia[485,])
#unique(Russia[,25]) "DE,SE: Inapplicable;RU: Inappropiate response;SG:Missing;HT: Dropped out survey"

#unique(Russia[,125]) #"HT: Dropped out survey; RU: Inappropriate response SG: Refused"

#HT: Missing; PS,SE: Inapplicable;RU: Inappropriate resp

#str_replace_all(string, pattern, replacement) 

#Russia %<>% rename() str_replace_all("Inappropriate", "No answer") 
```

```{r identifying which questions were Not asked in each country, include=FALSE}

findNotAskedQuestions <- function(dataSet){
  firstguy <- dataSet[1,] %>%as.character() %>% as.vector()
  notAskedNums = c()
  for(i in 1:length(firstguy)){
   if(firstguy[i] == "Not asked"){notAskedNums = c(notAskedNums, i)}
  }
  return (colnames(dataSet[notAskedNums]))
}

notAskedUS <- findNotAskedQuestions(US)
notAskedRussia <- findNotAskedQuestions(Russia)
notAskedJapan <- findNotAskedQuestions(Japan)

allNotAsked <- intersect(intersect(notAskedUS, notAskedRussia), notAskedJapan)

```

```{r identifying which questions are in venn diagram, include=FALSE}
###first remove the not asked questions 

#regets the numbers of the columns I want to toss 
usTossCols <- -1*c(which(colnames(US) %in% notAskedUS))
russiaTossCols <- -1*c(which(colnames(Russia) %in% notAskedRussia))
japanTossCols <- -1*c(which(colnames(Japan) %in% notAskedJapan))
#then tosses them DO NOT RUN THIS CODE MORE THAN ONCE OR YOU WILL LOOSE DATA 
US <- US[,usTossCols]
Russia <- Russia[,russiaTossCols]
Japan <- Japan[,japanTossCols]

### now finds the intersect of all three as well as just pairs of the countries 
interAll <- intersect(intersect(colnames(US), colnames(Russia)), colnames(Japan))
interUSRus <- intersect(colnames(US), colnames(Russia))
interUSJap <- intersect(colnames(US), colnames(Japan))
interRusJap <- intersect(colnames(Japan), colnames(Russia))

### and now the unique ones 
unionUS <- union(interUSRus, interUSJap) #union of all US shared ones
USUnique <- setdiff(colnames(US),unionUS) #unique US ones

unionRussia <- union(interUSRus, interRusJap) #union of all Russia shared ones 
RussiaUnique <- setdiff(colnames(Russia), unionRussia) #unique Russia ones 

unionJapan <- union(interUSJap, interRusJap) #union of all Japan shared ones 
JapanUnique <- setdiff(colnames(Japan), unionJapan) #unique Japan ones 

### and finally taking the union of all of them 
unionAll <- union(union(colnames(US), colnames(Russia)), colnames(Japan))

```

```{r cleaning for specific data point, include=FALSE}

#hasNoAnswer = c()
#for(i in 1:length(US[,1])){
#  if(sum(is.na(US[i,])) > 0){
 #   hasNoAnswer = c(hasNoAnswer,i)
#  }
#}
#hasNoAnswer

#so, I can't out right make no answer an NA and then just delete it because if I do then all of the data points will disappear
#therefore, Im going to have to do it when I call the graph on the specific variable 

```

```{r make all the factors because survey woohoo, include=FALSE}

#handwave everything to be factors, will go back and clean individual columns in a bit
US[,1:ncol(US)] <- lapply(US[,1:ncol(US)], as.factor)
Russia[,1:ncol(Russia)] <- lapply(Russia[,1:ncol(Russia)], as.factor)
Japan[,1:ncol(Japan)] <- lapply(Japan[,1:ncol(Japan)], as.factor)






```

```{r vectors for the options for questions part shiny app, include=FALSE}
uniqueOptions <- c("United States", "Russia", "Japan")
intersectionOptions <- c("All", "United States/Russia", "United States/Japan", "Russia/Japan")
notAskedOptions <- c("All", "United States", "Russia", "Japan")

allTheVectors <- c("Unique to US", "Unique to Russia", "Unique to Japan", 
                   "Intersection of All Three", "Intersection Between US and Russia", 
                   "Intersection Between US and Japan", "Intersection Between Russia and Japan",
                   "Not Asked at All", "Not Asked in US", "Not Asked in Russia","Not Asked in Japan")
```

```{r, include = FALSE}
#isolate the variables I want for each country 

USsmall <- US %>% select(interAll[c(7,42,176)])
RussiaSmall <- Russia %>% select(interAll[c(7,42,176)])
JapanSmall <- Japan %>% select(interAll[c(7,42,176)])

#now lets reorder the factors like I wanted to earlier 
happy = c("Not at all happy", "Not very happy", "Rather happy", "Very happy")
happy <- happy %>% factor(levels = happy, ordered = TRUE)

worry = c("Not at all", "Not much", "Very much", "A great deal")
worry <- worry %>% factor(levels = worry, ordered = TRUE)

agree <- c("Strongly disagree", "Disagree", "Neither", "Agree", "Agree strongly")
agree <- agree %>% factor(levels = agree, ordered = TRUE)



cleanFacts <- function(data){
#FIX HAPPY VARIABLES 
happy_cols <- colnames(data)[c(1)]
data <- data %>% mutate_at(vars(happy_cols),
                           ~replace(.,. %notin% happy, NA))
data %<>% mutate_at(happy_cols, funs(factor(.,levels = happy, ordered = TRUE)))

#FIX AGREE VARIABLES
agree_cols <- colnames(data)[c(2)]
data <- data %>% mutate_at(vars(agree_cols),
                           ~replace(.,. %notin% agree, NA))
data %<>% mutate_at(agree_cols, funs(factor(.,levels = agree, ordered = TRUE)))

#FIX THE WORRY VARIABLE
worry_cols <- colnames(data)[c(3)]
data <- data %>% mutate_at(vars(worry_cols),
                           ~replace(.,. %notin% worry, NA))
data %<>% mutate_at(worry_cols, funs(factor(.,levels = worry, ordered = TRUE)))

  return(data)
}

USsmall %<>% cleanFacts()%>%na.omit()
RussiaSmall %<>% cleanFacts()%>%na.omit()
JapanSmall %<>% cleanFacts()%>%na.omit()

View(RussiaSmall)

```




##What the World Values Survey Is

  >-an international to study how people's values change over time and the resulting impact on political and social aspects of a country
  
  >-distributed in nearly 100 countries
  
  >-explore the participants' views on democracy, tolerance, gender and race equality, religion, the environment, politics, famility, the community, etc
  
  >-data that can be analyzed to understand how people's beliefs, motivations, and values evolve between countries and over time and providing key insights to a multitude of different questions

##Goals for this Project
  >-performed simple Exploratory Data Analysis on WVS data sets from the United States, Russia, and Japan
  
  >-compared responses for individual questions and proportion of responses for pairs of variables
  
  >-explored differences in the survey questions that were asked among the three countries

##Cleaning 

>-removing columns with repetative, no longer necessary information

>-questions that were not asked in each country were identified, saved to vectors by name, and deleted from the main data frame

>-find the union of all questions asked, intersections among the combinations of countries, and questions unique for each country

>-each column of the data sets were set to be factors and reordered when necessary

##Single Variable Graphs 
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(USsmall, aes(x=USsmall[,1]))+
      geom_bar() +
      labs(x = "Feeling of Happiness", y = "Frequency", title='US')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(RussiaSmall, aes(x=RussiaSmall[,1]))+
      geom_bar() +
      labs(x = "Feeling of Happiness", y = "Frequency", title='Russia')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(JapanSmall, aes(x=JapanSmall[,1]))+
      geom_bar() +
      labs(x = "Feeling of Happiness", y = "Frequency", title='Japan')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(USsmall, aes(x=USsmall[,2]))+
      geom_bar() +
      labs(x = "Make My Parents Proud", y = "Frequency", title='US')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(RussiaSmall, aes(x=RussiaSmall[,2]))+
      geom_bar() +
      labs(x = "Make My Parents Proud", y = "Frequency", title='Russia')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(JapanSmall, aes(x=JapanSmall[,2]))+
      geom_bar() +
      labs(x = "Make My Parents Proud", y = "Frequency", title='Japan')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(USsmall, aes(x=USsmall[,3]))+
      geom_bar() +
      labs(x = "Worry About Giving Children Good Education", y = "Frequency", title='US')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(RussiaSmall, aes(x=RussiaSmall[,3]))+
      geom_bar() +
      labs(x = "Worry About Giving Children Good Education", y = "Frequency", title='Russia')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Single Variable Graphs
```{r, echo=FALSE, fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(JapanSmall, aes(x=JapanSmall[,3]))+
      geom_bar() +
      labs(x = "Worry About Giving Children Good Education", y = "Frequency", title='Japan')+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

##Double Variable Graphs - Happiness and Proud Parents
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
#AGREE AND HAPINESS 
ggplot(USsmall, aes(x=USsmall[,2], fill = USsmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Make My Parents Proud", y = "Proportion", title='US', fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Double Variable Graphs - Happiness and Proud Parents
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(RussiaSmall, aes(x=RussiaSmall[,2], fill = RussiaSmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Make My Parents Proud", y = "Proportion", title='Russia', fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Double Variable Graphs - Happiness and Proud Parents
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
#AGREE AND HAPINESS 
ggplot(JapanSmall, aes(x=JapanSmall[,2], fill = JapanSmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Make My Parents Proud", y = "Proportion", title='Japan', fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


##Double Variable Graphs - Happiness and Worries
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(USsmall, aes(x=USsmall[,3], fill = USsmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Worry About Giving Children Good Education", y = "Proportion", title="US", fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Double Variable Graphs - Happiness and Worries
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(RussiaSmall, aes(x=RussiaSmall[,3], fill = RussiaSmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Worry About Giving Children Good Education", y = "Proportion", title='Russia', fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Double Variable Graphs - Happiness and Worries
```{r , fig.width=7,fig.height=4.5, echo = FALSE, message = FALSE}
ggplot(JapanSmall, aes(x=JapanSmall[,3], fill = JapanSmall[,1]) ) +
      geom_bar(position = "fill") +
      scale_fill_viridis_d(option = "viridis") +
       labs(x = "Worry About Giving Children Good Education", y = "Proportion", title='Japan', fill = "Feeling of Happiness")+
      theme_minimal()+theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


##Question Sets 

Not Asked Observations:
  >- logically excluded such as a person’s confidence level on certain organizations that the three countries are not members since those do not pertain to those three countries

  >- additional personality traits, election integrity and government corruption  inquiries

Unique US: appropriate for the only North American country in the data set

Unique Russia: two of three relate to the Commonwealth of Independent States (CIS); third was prostitution

Unique Japan: additional questions specifically over the Aisan concerns; last was “It is important to this person to do something good for society”
  
##The End 

**Questions?**




